Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Remove a TODO

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
Maybe we cover the details in the \pv{} Voter discussion?}

>>>>

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
``mixnet.''
